Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-02-04 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
xxxx

@@

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(
    Group = factor(Group, levels = c("Novice", "Expert")),
    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management + 3 Items", "Presence", "Overall"))  # Reorder scales
  ) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

@@

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management + 3 Items", "Classroom Management + 3 Items")
t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")

@@

# Calculate omega for Classroom Management
omega_cm <- calculate_omega_total(df_cm, "Classroom Management + 3 Items")

@@

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management + 3 Items", "Presence"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
)

@@

# Data Import and Preprocessing ------------------------------------------
sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201, 223),  # Removing invalid IDs
    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
  ) %>%
  mutate(
    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
    ID = as.factor(ID)  # Ensure that ID is treated as a factor (if needed)
  )

@@

# Descriptive Statistics -------------------------------------------------
## Disruption Appraisal by Group
sri_disrup_table <- sri %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Disruption Appraisal by Disruption Category (Split by Novice and Expert)
sri_disrup_category_table <- df_sri_disrup %>%
  group_by(Group, Disruption_Category) %>%
  summarise(
    N = n(),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Disruption Appraisal for each disruption event
sri_disrup_single_table <- df_sri_disrup %>%
  group_by(Group, event) %>%
  summarise(
    N = n(),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal by Group
sri_confi_table <- sri %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal by Disruption Category (Split by Novice and Expert)
sri_confi_category_table <- df_sri_disrup %>%
  group_by(Group, Disruption_Category) %>%
  summarise(
    N = n(),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal for each disruption event
sri_confi_single_table <- df_sri_disrup %>%
  group_by(Group, event) %>%
  summarise(
    N = n(),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

## Prevalence Rating by Group
sri_preva_table <- sri %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
  )

## Prevalence Rating by Disruption Category (Split by Novice and Expert)
sri_preva_category_table <- df_sri_disrup %>%
  group_by(Group, Disruption_Category) %>%
  summarise(
    N = n(),
    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
  )

## Prevalence Rating for each disruption event
sri_preva_single_table <- sri %>%
  group_by(Group, event) %>%
  summarise(
    N = n(),
    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
  )

@@

## Prevalence Rating by Group
kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

## Prevalence Rating by Disruption Category (Split by Novice and Expert)
kable(sri_preva_category_table, caption = "Descriptive Statistics for Prevalence Rating by Disruption Category", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

## Prevalence Rating for each disruption event (Sorted by Mean)
kable(sri_preva_single_table_sorted, caption = "Descriptive Statistics for Prevalence Rating by Disruption Event (Sorted by Mean)", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

@@

## Prevalence Rating
preva_plot <- sri %>%
  ggplot(aes(x = Group, y = prevalence_rating, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
  labs(x = "", y = "Prevalence Rating") +
  scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
  ggtitle("Prevalence Rating by Group") +
  theme_cowplot() +
  theme(legend.position = "none")  # No legend for the main plot

print(preva_plot)

## Prevalence Rating by Disruption Category, Split by ID (Novice vs Expert)
preva_cat_plot <- df_sri_disrup %>%
  ggplot(aes(x = Disruption_Category, y = prevalence_rating, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
  labs(x = "", y = "Prevalence Rating") +
  scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in preva_plot
  ggtitle("Prevalence Rating by Disruption Category") +
  theme_cowplot() +
  theme(legend.position = "top") +  # Place the legend at the top
  scale_fill_discrete(name = "Group")  # Add a title to the legend

print(preva_cat_plot)

@@

# Omega Calculations -----------------------------------------------------
# Data Import
sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201, 223), # Exclude specific IDs
    !disruption_appraisal %in% c(-100, -99, -88),
    !confidence_appraisal %in% c(-100, -99, -88),
    !prevalence_rating %in% c(-100, -99, -88)
  )

@@

# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Student --------------------------------------------
df_aoi_numb_dur <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    Duration_of_interval  # Ensure this variable is included
  ) %>%
  dplyr::select(
    -contains("Disruptive_Person")  # Exclude Disruptive Student
  ) %>%
  rowwise() %>%
  transmute(
    Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
                                      Duration_of_interval_min, 0),
    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
  ) %>%
  select(Participant,
        Number_fixation_min_mtu,
        Average_duration_mtu,
        GRI_mtu) %>% 
  arrange(Participant)

# ET-Measures (AOI Students) - Exclude Disruptive Student --------------------------------------------
df_aoi_stud <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
  ) %>%
  select(Participant,
         Stud_number_fixation_min,
         Average_duration_stud
         ) %>% 
  arrange(Participant) %>% 
  drop_na()

@@

# Number of fixations per second and Average duration of fixations --------------------------------------------
# Define the different types of disruptions and categories
disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
                 "Drumming_with_hands", "Head_on_table", "Heckling", 
                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")

# Step 1: Filter and prepare the data for both fixation counts and average durations
df_aoi_disrup <- df_aoi %>%
  filter(TOI %in% disruptions) %>%  # Filter rows based on the disruption list
  select(Group, Participant, TOI, 
         Duration_of_interval, 
         "Number_of_fixations.Disruptive_Person", 
         "Total_duration_of_fixations.Disruptive_Person") %>%
  mutate(
    Group = as_factor(Group),  # Convert Group column to a factor
    Disruption_Category = case_when(  # Assign categories based on disruption type
      TOI %in% verbal_disruptions ~ "Verbal disruptions",
      TOI %in% physical_disruptions ~ "Physical disruptions",
      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
      TRUE ~ NA_character_
    ),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),  # Convert duration to seconds
    Disrup_average_fixations = round(Total_duration_of_fixations.Disruptive_Person / 
                                     `Number_of_fixations.Disruptive_Person`, 2)  # Average duration in seconds
  ) %>%
  filter(!is.na(Disruption_Category))  # Remove rows with NA in disruption category

# Step 2: Summarize data by disruption category
disruption_summary <- df_aoi_disrup %>%
  group_by(Group, Participant, Disruption_Category) %>%
  summarise(
    total_duration_sec = round(sum(Duration_of_interval_sec, na.rm = TRUE), 2),  # Total time in seconds
    fixation_count = round(sum(`Number_of_fixations.Disruptive_Person`, na.rm = TRUE), 2),  # Total fixations
    Disrup_fixations_per_second = round(fixation_count / total_duration_sec, 2),  # Number of Fixation per second
    Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Average disruption fixations duration
    .groups = "drop"
  )

# Step 3: Summarize by participant
df_aoi_disrup <- disruption_summary %>%
  group_by(Group, Participant) %>%
  summarise(
    Disrup_fixations_per_second = round(mean(Disrup_fixations_per_second, na.rm = TRUE), 2),  # Mean Number of Fixation per participant
    Disrup_average_fixations = round(mean(Disrup_average_fixations, na.rm = TRUE), 2),  # Mean disruption fixation duration per participant
    .groups = "drop"
  ) %>% 
  select(Participant, Disrup_fixations_per_second, Disrup_average_fixations) %>%  # Select only relevant columns
  arrange(Participant)

# Time to first fixation on AOI Disruptive Student --------------------------------------------
# Step 1: Data Preparation
df_ttff_disrup <- df_aoi %>%
  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
  dplyr::select(
    Participant,
    TOI,
    Time_to_first_fixation.Disruptive_Person
  ) %>%
  mutate(
    Group = ifelse(Participant < 200, "Novice", "Expert"),  # Assigning Group based on Participant
    Disruption_Category = case_when(
      TOI %in% verbal_disruptions ~ "Verbal disruptions",
      TOI %in% physical_disruptions ~ "Physical disruptions",
      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
  drop_na() %>%
  filter(
    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
  ) %>%
  mutate(
    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
  )

# Summarize the Disrup_time_fixation_sec by Participant
df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
  group_by(Participant) %>%
  summarise(
    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
    .groups = "drop"
  ) %>% 
  arrange(Participant)

# SRI Rating Data --------------------------------------------
# Data Import and Preprocessing ------------------------------------------
df_sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201, 223),  # Removing invalid IDs
    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
  ) %>%
  mutate(
    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
    Participant = ID,  # Keep ID as is for Participant column
    Disruption_Appraisal = as.numeric(disruption_appraisal),
    Confidence_Appraisal = as.numeric(confidence_appraisal),
    Prevalence_Rating = as.numeric(prevalence_rating)
  ) %>%
  select(-ID) %>% # Remove the original ID column after renaming
  arrange(Participant)

@@

# Step 1: Filter for specific disruptions
verbal_disruptions <- c("whispering", "chatting")
lack_of_eagerness <- c("drawing", "looking at phone")

>>>>

# Create APA-Conform Table for Overall Evaluation
overall_summary <- df_quest_long %>%
  filter(`Scales Self-evaluation` == "Overall") %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(Mean, na.rm = TRUE), 2),
    SD = round(sd(Mean, na.rm = TRUE), 2),
    Min = round(min(Mean, na.rm = TRUE), 2),
    Max = round(max(Mean, na.rm = TRUE), 2)
  )

# Display the table in APA format
kable(overall_summary, caption = "Descriptive Statistics for Overall Evaluation") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

@@

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(
    Group = factor(Group, levels = c("Novice", "Expert")),
    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
  ) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

@@

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")

@@

# Calculate omega for Classroom Management
omega_cm <- calculate_omega_total(df_cm, "Classroom Management")

@@

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management", "Presence"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
)

@@

# Read the dataset
sri <- read_excel("data/Coding_SRI.xlsx") %>%
  filter(
    !ID %in% c(201, 223),  # Removing invalid IDs
    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
  ) %>%
  mutate(
    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
    ID = as.factor(ID)  # Convert ID to factor if needed
  )

@@

# Descriptive Statistics -------------------------------------------------
## Disruption Appraisal by Group
sri_disrup_table <- sri %>%
  group_by(Group) %>%
  summarise(
    n_distinct(ID),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Disruption Appraisal by Disruption Category (Split by Novice and Expert)
sri_disrup_category_table <- df_sri_disrup %>%
  group_by(Group, Disruption_Category) %>%
  summarise(
    n_distinct(ID),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Disruption Appraisal for each disruption event
sri_disrup_single_table <- df_sri_disrup %>%
  group_by(Group, event) %>%
  summarise(
    n_distinct(ID),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal by Group
sri_confi_table <- sri %>%
  group_by(Group) %>%
  summarise(
    n_distinct(ID),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal by Disruption Category (Split by Novice and Expert)
sri_confi_category_table <- df_sri_disrup %>%
  group_by(Group, Disruption_Category) %>%
  summarise(
    n_distinct(ID),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal for each disruption event
sri_confi_single_table <- df_sri_disrup %>%
  group_by(Group, event) %>%
  summarise(
    n_distinct(ID),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

# ## Prevalence Rating by Group
# sri_preva_table <- sri %>%
#   group_by(Group) %>%
#   summarise(
#     n_distinct(ID),
#     M = round(mean(prevalence_rating, na.rm = TRUE), 2),
#     SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
#     Min = round(min(prevalence_rating, na.rm = TRUE), 2),
#     Max = round(max(prevalence_rating, na.rm = TRUE), 2)
#   )
# 
# ## Prevalence Rating by Disruption Category (Split by Novice and Expert)
# sri_preva_category_table <- df_sri_disrup %>%
#   group_by(Group, Disruption_Category) %>%
#   summarise(
#     n_distinct(ID),
#     M = round(mean(prevalence_rating, na.rm = TRUE), 2),
#     SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
#     Min = round(min(prevalence_rating, na.rm = TRUE), 2),
#     Max = round(max(prevalence_rating, na.rm = TRUE), 2)
#   )
# 
# ## Prevalence Rating for each disruption event
# sri_preva_single_table <- sri %>%
#   group_by(Group, event) %>%
#   summarise(
#     N = n(),
#     M = round(mean(prevalence_rating, na.rm = TRUE), 2),
#     SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
#     Min = round(min(prevalence_rating, na.rm = TRUE), 2),
#     Max = round(max(prevalence_rating, na.rm = TRUE), 2)
#   )

@@

# ## Prevalence Rating by Group
# kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
# 
# ## Prevalence Rating by Disruption Category (Split by Novice and Expert)
# kable(sri_preva_category_table, caption = "Descriptive Statistics for Prevalence Rating by Disruption Category", digits = 2) %>%
#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
# 
# ## Prevalence Rating for each disruption event (Sorted by Mean)
# kable(sri_preva_single_table_sorted, caption = "Descriptive Statistics for Prevalence Rating by Disruption Event (Sorted by Mean)", digits = 2) %>%
#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

@@

# ## Prevalence Rating
# preva_plot <- sri %>%
#   ggplot(aes(x = Group, y = prevalence_rating, fill = Group)) +
#   geom_boxplot(outlier.shape = NA) +
#   geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
#   labs(x = "", y = "Prevalence Rating") +
#   scale_fill_brewer(palette = "RdBu") +  # Using the RdBu color palette for Novice and Expert
#   ggtitle("Prevalence Rating by Group") +
#   theme_cowplot() +
#   theme(legend.position = "none")  # No legend for the main plot
# 
# print(preva_plot)
# 
# ## Prevalence Rating by Disruption Category, Split by ID (Novice vs Expert)
# preva_cat_plot <- df_sri_disrup %>%
#   ggplot(aes(x = Disruption_Category, y = prevalence_rating, fill = Group)) +
#   geom_boxplot(outlier.shape = NA) +
#   geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
#   labs(x = "", y = "Prevalence Rating") +
#   scale_fill_brewer(palette = "RdBu") +  # Use the same RdBu color palette as in preva_plot
#   ggtitle("Prevalence Rating by Disruption Category") +
#   theme_cowplot() +
#   theme(legend.position = "top") +  # Place the legend at the top
#   scale_fill_discrete(name = "Group")  # Add a title to the legend
# 
# print(preva_cat_plot)

# Ensure no duplicates (keeping one row per participant)
sri_clean <- sri %>%
  group_by(ID) %>%
  summarise(
    Group = first(Group),
    disruption_appraisal = mean(disruption_appraisal, na.rm = TRUE),
    confidence_appraisal = mean(confidence_appraisal, na.rm = TRUE)
  ) %>%
  ungroup()

# Check the number of unique participants
print(nrow(sri_clean))  # Should be 82

# t-Test for Disruption Appraisal
t_test_disrup <- t.test(disruption_appraisal ~ Group, data = sri_clean, var.equal = TRUE)
cohen_d_disrup <- cohen.d(disruption_appraisal ~ Group, data = sri_clean)

# t-Test for Confidence Appraisal
t_test_confi <- t.test(confidence_appraisal ~ Group, data = sri_clean, var.equal = TRUE)
cohen_d_confi <- cohen.d(confidence_appraisal ~ Group, data = sri_clean)

# Create APA-Formatted Table
t_test_results <- data.frame(
  "Group Comparison" = c("Experienced vs. Inexperienced", "Experienced vs. Inexperienced"),
  "Variable" = c("Disruption Appraisal", "Confidence Appraisal"),
  "t-value" = round(c(t_test_disrup$statistic, t_test_confi$statistic), 2),
  "df" = c(t_test_disrup$parameter, t_test_confi$parameter),
  "p-value" = format.pval(c(t_test_disrup$p.value, t_test_confi$p.value), digits = 3, eps = .001),
  "Mean Difference" = round(c(
    diff(t_test_disrup$estimate), 
    diff(t_test_confi$estimate)
  ), 2),
  "Cohen's d" = round(c(cohen_d_disrup$estimate, cohen_d_confi$estimate), 2),
  "95% CI (d)" = c(
    paste0("[", round(cohen_d_disrup$conf.int[1], 2), ", ", round(cohen_d_disrup$conf.int[2], 2), "]"),
    paste0("[", round(cohen_d_confi$conf.int[1], 2), ", ", round(cohen_d_confi$conf.int[2], 2), "]")
  )
)

# Print APA-formatted Table
knitr::kable(t_test_results, caption = "t-Test and Effect Sizes for Disruption and Confidence Ratings") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

# Omega Calculations -----------------------------------------------------
# Data Import
sri <- read_excel("data/Coding_SRI.xlsx") %>%
  filter(
    !ID %in% c(201, 223), # Exclude specific IDs
    !disruption_appraisal %in% c(-100, -99, -88),
    !confidence_appraisal %in% c(-100, -99, -88),
    !prevalence_rating %in% c(-100, -99, -88)
  )

@@

# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Student --------------------------------------------
df_aoi_numb_dur <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    Duration_of_interval  # Ensure this variable is included
  ) %>%
  dplyr::select(
    -contains("Disruptive_Person")  # Exclude Disruptive Student
  ) %>%
  rowwise() %>%
  transmute(
    Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
                                      Duration_of_interval_min, 0),
    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
    GRI = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
  ) %>%
  select(Participant,
        Number_fixation_min_mtu,
        Average_duration_mtu,
        GRI) %>% 
  arrange(Participant)

# ET-Measures (AOI Students) - Exclude Disruptive Student --------------------------------------------
df_aoi_stud <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
  ) %>%
  select(Participant,
         Stud_number_fixation_min,
         ) %>% 
  arrange(Participant) %>% 
  drop_na()

@@

# Time to first fixation on AOI Disruptive Student --------------------------------------------

# Summarize the log-transformed variable by Participant
df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
  group_by(Participant) %>%
  summarise(
    log_Disrup_time_fixation_sec = round(mean(log_Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average log time to first fixation per participant
    .groups = "drop"
  )

# SRI Rating Data --------------------------------------------
# Data Import and Preprocessing ------------------------------------------
df_sri <- read_excel("data/Coding_SRI.xlsx") %>%
  filter(
    !ID %in% c(201, 223),  # Removing invalid IDs
    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
  ) %>%
  mutate(
    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
    Participant = ID,  # Keep ID as is for Participant column
    Disruption_Rating = as.numeric(disruption_appraisal),
    Confidence_Rating = as.numeric(confidence_appraisal),
    Prevalence_Rating = as.numeric(prevalence_rating)
  ) %>%
  select(-ID) %>% # Remove the original ID column after renaming
  arrange(Participant)

@@

# Step 1: Summarize appraisals for each disruption
df_sri_disrup_summary <- df_sri %>%
  filter(event %in% c(verbal_disruptions, lack_of_eagerness)) %>%
  group_by(Participant, event) %>%
  summarise(
    Disruption_Appraisal_Mean = mean(disruption_appraisal, na.rm = TRUE),
    Confidence_Appraisal_Mean = mean(confidence_appraisal, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = event,
    values_from = c(Disruption_Appraisal_Mean, Confidence_Appraisal_Mean),
    names_sep = "_"
  ) %>%
  mutate(across(everything(), ~ replace_na(., 0))) %>%   # Replace missing values with 0
  arrange(Participant)

# Step 2: Summarize overall appraisals by Participant
df_sri_clean <- df_sri %>%
  group_by(Participant) %>%
  summarise(
    Disruption_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
    Confidence_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  arrange(Participant)
